Stepwise Multiple Regressions

### 2021-02-27 Stepwise Multiple Regressions.Rmd
simulated distributions

---
title: "Stepwise Multiple Regressions"
author: "Leah Thornton Hampton"
date: "2/1/2021"
output:
  html_document: 
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 4
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE, echo = FALSE)
```
---

>>>>

---
title: "Stepwise Multiple Regressions"
author: "Leah Thornton Hampton"
date: "2/1/2021"
output:
  html_document: 
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 4
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE)
```
---
